### 2019-07-06 thesis-template/msc-thesis.tex
update

\begin{figure}[!t]
\centering
  \begin{minipage}{0.29\textwidth}
  \includegraphics[height=\textwidth]{img/star.png}
    \caption*{\enquote{Star} test field}
    \label{a)}
  \end{minipage}
  \begin{minipage}{0.29\textwidth}
    \includegraphics[height=\textwidth]{img/star_ftle.PNG}
     \caption*{LTG slice($90^\circ$)}
    \label{b)}
  \end{minipage}
  \begin{minipage}{0.35\textwidth}
  \centering
    \includegraphics[height=\textwidth]{img/star_volume_alt.PNG}
     \caption*{IsoVolume on LTG volume}
    \label{b)}
  \end{minipage}
  \caption{LTG on \enquote{star} test field}
\label{star-ftle}
\end{figure}
When we look at the example depicted in Fig. \ref{star-ftle}, we can see the FTLE approach LTG responding most in the center of the field, which is the knot point of tensor field lines diverging in any direction. Remark, that in the middle image there is a light V-shaped ridge on the left on blue background which is outshined by the center spot because of its orders of larger magnitude. The volume illustrated on the right even shows a spiked structure for the volume representing all directions at once. The approach detects more ridges in diagonal directions stochastically as we can infer from the Gaussian-shaped plates in the thresholded volume, evenly spaced in $90^\circ$ shifts with $45^\circ$ (quarter volume) offset. These can be interpreted nicely, since the diagonal direction is never offset into its transmission direction leading to a trivial (none) difference for axis-parallel directions for the offset direction orthogonal to the light source direction. Hence, the differences will be factor $2$ at worst for the diagonals, since we measure differences in both offset directions, in case ridges in both axis-parallel and -diagonal directions are present. Accordingly, we observe Gaussian-plates in the volume instead of sharp, contrasted ridges for the \enquote{star} example. But wouldn't we expect a ridges only in parallel directions? Well, in this case, we could imagine not only tensor field lines diverge or converge, but also they could cross each other unaffectedly (just as with light paths), which could be the case when shifting away from the diagonal directions. For better imagination, offset the light source vertically or horizontally from the diagonals and observe the light paths hitting the axes (, which in fact do cross each other).

@@

 We will now capture the star dataset revealing tensor field lines diverging in any direction from the center.
Now, we will evaluate a classic textbook example called the \enquote{double gyre} \cite{shawn}, which is a quadruple gyre in our case for formatting reasons, yet yielding the same conceptual results. We compare the glyph representation to the LTG magnitude for a single slice ($0^\circ$) again:
\begin{figure}[!t]
\centering
  \begin{minipage}[t]{0.3\textwidth}
  \includegraphics[height=\textwidth]{img/gyre.png}
    \caption*{a) Glyphs}
    \label{a)}
  \end{minipage}
  \begin{minipage}[t]{0.3\textwidth}
    \includegraphics[height=\textwidth]{img/gyre_ftle.PNG}
     \caption*{b) LTG}
    \label{b)}
  \end{minipage}
  \begin{minipage}[t]{0.3\textwidth}
    \includegraphics[height=\textwidth]{img/gyre_ftle_org.PNG}
     \caption*{c) FTLE: Hlawatsch's approach}
    \label{b)}
  \end{minipage}
  \caption{Gyre test field}
\label{gyre-ftle}
\end{figure}
We can observe the method segmenting ridges in local ROIs exhibiting diverging tensor field lines w.r.t. the $x$-axis ($0^\circ$). Note that even regions in antiparallel directions ridgres are detected to (literally) some degree: Remark the ridges being contiguos lines at the level of the gyre centers where converging turns into diverging. Again, it is noticeable, that the results correspond to each other to a certain degree. This implies, that we obtained reasonable results generated by our method, but the classical tensor field line FTLE is more strict concerning its directive abilities and congruently does not do things by halves (like we do with our partitioned light distributions). Also remember, that the resulting ridges are not to be concerned sharp ones, since we measure the separation of whole light distributions, which should be considered a continous response or measure. We again depict volume representations for this example:
\begin{figure}[!t]
\centering
  \begin{minipage}{0.3\textwidth}
  \includegraphics[height=\textwidth]{img/gyre_volume2.png}
    \caption*{a) IsoVolume}
    \label{a)}
  \end{minipage}
  \begin{minipage}{0.3\textwidth}
    \includegraphics[height=\textwidth]{img/gyre_gauss_contour.PNG}
     \caption*{b) Contour}
    \label{b)}
  \end{minipage}
   \begin{minipage}{0.3\textwidth}
    \includegraphics[height=\textwidth]{img/gyre_volume4.PNG}
     \caption*{c) GaussContour}
    \label{b)}
  \end{minipage}
  \caption{\enquote{Gyre} test field}
\label{gyre_volume}
\end{figure}
When we consider the volumes for the \enquote{gyre} test field, we can remark the holes, which represent the gyres in the centers of the volume for a low and a high threshold, whereby we extract (filter out) the previously observed ridges in $3D$ for all directions $\omega$ simultaneously.

Now, that the approach has passed the textbook examples, we push it forward to be applied in real (measured) data to show its performance in discerning and segmenting ROIs from a human brain. The approach will detect LCS in the brain's tissue from MRI-measured diffusion tensors of a male subject at the age of 27. We compare ParaView's glyph representation to the FTLE method LTG for the test field \enquote{brain}:
\begin{figure}[!t]
\centering
  \begin{minipage}[t]{0.3\textwidth}
  \includegraphics[height=\textwidth]{img/brain_cyl_glyphs.PNG}
    \caption*{a) glyph representation}
    \label{a)}
  \end{minipage}
  \begin{minipage}[t]{0.3\textwidth}
    \includegraphics[height=\textwidth]{img/brain_ftle.PNG}
     \caption*{b) LTG}
    \label{b)}
  \end{minipage}
  \begin{minipage}[t]{0.3\textwidth}
    \includegraphics[height=\textwidth]{img/brain_ftle_org.PNG}
     \caption*{c) FTLE: Hlawatsch's approach}
    \label{b)}
  \end{minipage}
  \caption{\enquote{Brain} test field}
\label{brain-ftle}
\end{figure}
Regarding Fig. \ref{gyre_volume}, we find that the approach detects the boundaries of concavities (lat.: Gyri) in the brain, forming the lobus cerebri (commonly known a lobes). The invented method could thus, e.g., aid to compute $3D$ models of a subject in medical sciences. It emphasizes regions with increased change in flow-rate (throughput), because in this areas the anisotropy and/or tensor magnitude is increased, preventing the intensities from being absorbed, hence yielding to a high FTLE-response. The regions highlighted in red, are caused by high tensor magnitudes, as we can infer from the glyph representation revealing no linear anisotropy at all. Note that we do not show the volume representation in this case, since all directions (slices) look approximately the same because the tensor field is only introducing changes in tensor magnitude not in anisotropy as inferred from the glyph representation. The regions with a tensor magnitude higher than zero restrict the light propagation to certain areas with the condition, that not all of the energy is absorbed by sorrounding cells in the local neighborhood. Again comparing the results to the classical FTLE (Hlawatsch's approach) on tensor fields in Fig. \ref{brain_ftle_comp}, we notice that the FTLE response is chaotic, since this MRI scan is subject to inherent MRI noise filling the background regions in the image. This noise produces random trajectories, leading to an increased gradient of the flow map and thus to a high FTLE response, which reveals trajectories running in random directions in background regions. Only in foreground regions, the trajectories are directed in definite manner, which is why the flow map's gradient is minimized along the brain structure (foreground, depicted in blue in Fig \ref{brain_ftle_comp} c)). Yet, our approach uses absorption to decrease noise present in the tensor field and reasonable min-max scaling to conduct $100\%$ of the intensity for the cell with the highest tensor magnitude. Hence, we do not yield a noisy representation but a FG-BG segmented image, with red highlights in positions, where the tensor magnitude is maximized (and thus absorption is minimized). Remark, that the resulting volume does not inherently depend on the direction, because the test field does not introduce any strong linear anisotropy, as visible from the glyph representation in Fig. \ref{brain_ftle_comp} a). If no linear anisotropy was incorporated, the FTLE response will also be independent on the direction to the greatest extent. The slices we obtain as our volume are, with reasonable explanation, more or less identical comparing them against each other for certain directions.

@@

\begin{figure}[!t]
\centering
  \begin{minipage}{0.3\textwidth}
  \centering
  \includegraphics[height=\textwidth]{img/heart_org.PNG}
    \caption*{a) tensor magnitude}
    \label{a)}
  \end{minipage}
  \begin{minipage}{0.3\textwidth}
  \centering
    \includegraphics[height=\textwidth]{img/heart.PNG}
     \caption*{b) LTG}
    \label{b)}
  \end{minipage}
  \begin{minipage}{0.3\textwidth}
  \centering
    \includegraphics[height=\textwidth]{img/heart_ftle_org.PNG}
     \caption*{c) Hlawatsch's approach}
    \label{b)}
  \end{minipage}
  \caption{\enquote{heart} test field}
\label{heart-ftle}
\end{figure}
After applying the LTG approach on the heart dataset, we observe the resulting tensor magnitude weighted FTLE-field, which is again not changing w.r.t. direction, which is why we do not show the volumes. The approach highlights the regions with diverging tensor field lines resulting from linear anisotropy or increased tensor magnitude, emerging as ridges. These ridges could now represent blood vessels and such. The red spot emphasized in the left of the image could, e.g., represent the highest diffusion velocity in tissue. When considering the FTLE for the heart dataset depicted in Fig. \ref{heart-ftle-comp}, we find that the trajectories exhibit strong correlations amongst them. This results from the low noise rate inherently present in this dataset. The inital value for our angle is given by $0$ degree, which is why the trajectories follow this angle strictly in case of a zero matrix (corresponding to a noise free cell in background regions). In this case, we obtain the same results as the approach from Hlawatsch et al., whereas our global min-max normalization (due to noise) is becoming a redundant step for noiseless input data. A proof of this elaboration can be found in Fig. \ref{heart-ftle-comp}.

@@

\begin{figure}[!t]
\centering
  \begin{minipage}{0.4\textwidth}
   \centering
  \includegraphics[width=\textwidth]{img_new/random-global.png}
    \caption*{Global normalization}
    \label{a)}
  \end{minipage}
  \begin{minipage}{0.4\textwidth}
   \centering
    \includegraphics[width=\textwidth]{img_new/random-local.PNG}
     \caption*{Local normalization}
    \label{b)}
  \end{minipage}
\caption{\enquote{Random} test field}
\label{random}
\end{figure}
Observing the generated random test field both with global and local normalization in Fig. \ref{random}a)\& b) respectively, we remark that the propability for small numbers to have a high ratio in combination is increased, as linear anisotropy occurs mainly in BG regions (low tensor magnitudes). In case we use global normalization, we will again obtain a FTLE field independent on the direction, since tensor magnitudes outshine the changes in anisotropy in this test case.
\begin{figure}[!t]
\centering
  \begin{minipage}{0.4\textwidth}
   \centering
  \includegraphics[width=\textwidth]{img_new/random_global.png}
    \caption*{Global normalization}
    \label{a)}
  \end{minipage}
  \begin{minipage}{0.4\textwidth}
   \centering
    \includegraphics[width=\textwidth]{img_new/random_local_slice0.PNG}
     \caption*{Local normalization}
    \label{b)}
  \end{minipage}
\caption{\enquote{Random} test field}
\label{random}
\end{figure}
In case we use local normalization, we could interpret the contributions revealing low tensor magnitudes as a result from white noise, which shows the inherent problem with local normalization.

@@

Please note that all values in the test table where measured on following system:\\
\texttt{4 x 16-Core Gold 6142M 2.60GHz, 3072 GB RAM}.
\begin{table}
\small
\centering
\caption{Test Table LTG:}
\begin{tabularx}{\columnwidth}{X|X|X|X}
\hline\hline
test name - Fig. \# & resolution ($x\times y\times\omega$) & runtime $[s]$ & memory consumption\\
\toprule
\enquote{drain} - \ref{ftle_base} & $101\times101\times64=652864$ & $179878$ & $8\times652864\times 8\mathop{byte} +(101\times101 + 19\times64)\times8\mathop{byte}\approx47.02\mathop{MB}$\\ 
\hline 
\enquote{inverse} - \ref{inverse-ftle} & $101\times101\times64=652864$ & $68787$ & $8\times652864\times 8\mathop{byte} +(101\times101 + 19\times64)\times8\mathop{byte}\approx47.02\mathop{MB}$\\
\hline 
 &  &  & \\ 
\hline 
\enquote{isotropic} - \ref{bow-ftle} & $51\times51\times3283232$ & $1357$ & $8\times83232\times 8\mathop{byte} +(51\times51 + 19\times32)\times8\mathop{byte}\approx5.998\mathop{MB}$\\ 
\hline
\enquote{rings} - \ref{bow-ftle} & $51\times51\times32=83232$ & $5761$ & $8\times83232\times 8\mathop{byte} +(51\times51 + 19\times32)\times8\mathop{byte}\approx5.998\mathop{MB}$\\ 
\hline 
\enquote{bow} - \ref{bow-ftle} & $51\times51\times32=83232$ & $6128$ & $8\times83232\times 8\mathop{byte} +(51\times51 + 19\times32)\times8\mathop{byte}\approx5.998\mathop{MB}$\\ 
\hline 
\enquote{star} - \ref{star-ftle} & $51\times51\times32=83232$ & $5815$ & $8\times83232\times 8\mathop{byte} +(51\times51 + 19\times32)\times8\mathop{byte}\approx5.998\mathop{MB}$\\ 
\hline 
\enquote{inverse} - \ref{inverse-ftle} & $101\times101\times16=163216$ & $12308$ & $8\times163216\times 8\mathop{byte} +(101\times101 + 19\times16)\times8\mathop{byte}\approx11.754\mathop{MB}$\\ 
\hline 
\enquote{inverse} - \ref{inverse-ftle} & $101\times101\times32=326432$ & $24571$ & $8\times326432\times 8\mathop{byte} +(101\times101 + 19\times32)\times8\mathop{byte}\approx23.5\mathop{MB}$\\ 
\hline
\enquote{brain} - \ref{brain-ftle} & $128\times128\times64=1048576$ & $2427$ & $8\times1048576\times 8\mathop{byte} +(128\times128 + 19\times64)\times8\mathop{byte}\approx75.5\mathop{MB}$\\
\hline
\enquote{heart} - \ref{heart-ftle} & $256\times256\times32=2097152$ & $117199$ & $8\times2097152\times 8\mathop{byte} +(256\times256 + 19\times32)\times8\mathop{byte}\approx151.0\mathop{MB}$\\
\hline 
\end{tabularx}
   \vskip 1pt
\end{table}

>>>>

\begin{figure}[!t]
\centering
  \begin{minipage}{0.29\textwidth}
  \includegraphics[height=\textwidth]{img/star.png}
    \caption*{\enquote{Star} test field}
    \label{a)}
  \end{minipage}
  \begin{minipage}{0.29\textwidth}
    \includegraphics[height=\textwidth]{img/star_ftle.PNG}
     \caption*{LTG slice($0^\circ$)}
    \label{b)}
  \end{minipage}
  \begin{minipage}{0.35\textwidth}
  \centering
    \includegraphics[height=\textwidth]{img/star_volume_alt.PNG}
     \caption*{IsoVolume on LTG volume}
    \label{b)}
  \end{minipage}
  \caption{LTG on \enquote{star} test field}
\label{star-ftle}
\end{figure}
When we look at the example depicted in Fig. \ref{star-ftle}, we can see the FTLE approach LTG responding most in the center of the field, which is the knot point of tensor field lines diverging in any direction. Remark, that in the middle image there is a light V-shaped ridge on the left on blue background which is outshined by the center spot because of its orders of larger magnitude. The volume illustrated on the right even shows a spiked structure for the volume representing all directions at once. The approach detects more ridges in diagonal directions stochastically as we can infer from the Gaussian-shaped plates in the thresholded volume, evenly spaced in $90^\circ$ shifts with $45^\circ$ (quarter volume) offset. These can be interpreted nicely, since the diagonal direction is never offset into its transmission direction leading to a trivial (none) difference for axis-parallel directions for the offset direction orthogonal to the light source direction. Hence, the differences will be factor $2$ at worst for the diagonals, since we measure differences in both offset directions, in case ridges in both axis-parallel and -diagonal directions are present. Accordingly, we observe Gaussian-plates in the volume instead of sharp, contrasted ridges for the \enquote{star} example. But wouldn't we expect a ridges only in parallel directions? Well, in this case, we could imagine not only tensor field lines diverge or converge, but also they could cross each other unaffectedly (just as with light paths), which could be the case when shifting away from the diagonal directions. For better imagination, offset the light source vertically or horizontally from the diagonals and observe the light paths hitting the axes (, which in fact do cross each other).

@@

 We will now capture the star dataset revealing tensor field lines diverging in any direction from the center.
Now, we will evaluate a classic textbook example called the \enquote{double gyre} \cite{shawn}, which is a quadruple gyre in our case for formatting reasons, yet yielding the same conceptual results. We compare the glyph representation to the LTG magnitude for a single slice ($0^\circ$) again:
\begin{figure}[!t]
\centering
  \begin{minipage}[t]{0.3\textwidth}
  \includegraphics[height=\textwidth]{img/gyre.png}
    \caption*{a) Glyphs}
    \label{a)}
  \end{minipage}
  \begin{minipage}[t]{0.3\textwidth}
    \includegraphics[height=\textwidth]{img/gyre_ftle.PNG}
     \caption*{b) LTG($0^\circ$)}
    \label{b)}
  \end{minipage}
  \begin{minipage}[t]{0.3\textwidth}
    \includegraphics[height=\textwidth]{img/gyre_ftle_org.PNG}
     \caption*{c) FTLE: Hlawatsch's approach}
    \label{b)}
  \end{minipage}
  \caption{Gyre test field}
\label{gyre-ftle}
\end{figure}
We can observe the method segmenting ridges in local ROIs exhibiting diverging tensor field lines w.r.t. the $x$-axis ($0^\circ$). Note that even regions in antiparallel directions ridgres are detected to (literally) some degree: Remark the ridges being contiguos lines at the level of the gyre centers where converging turns into diverging. Again, it is noticeable, that the results correspond to each other to a certain degree. This implies, that we obtained reasonable results generated by our method, but the classical tensor field line FTLE is more strict concerning its directive abilities and congruently does not do things by halves (like we do with our partitioned light distributions). Also remember, that the resulting ridges are not to be concerned sharp ones, since we measure the separation of whole light distributions, which should be considered a continous response or measure. We again depict volume representations for this example:
\begin{figure}[!t]
\centering
  \begin{minipage}{0.3\textwidth}
  \includegraphics[height=\textwidth]{img/gyre_volume2.png}
    \caption*{a) IsoVolume}
    \label{a)}
  \end{minipage}
  \begin{minipage}{0.3\textwidth}
    \includegraphics[height=\textwidth]{img/gyre_gauss_contour.PNG}
     \caption*{b) Contour}
    \label{b)}
  \end{minipage}
   \begin{minipage}{0.3\textwidth}
    \includegraphics[height=\textwidth]{img/gyre_volume4.PNG}
     \caption*{c) GaussContour}
    \label{b)}
  \end{minipage}
  \caption{\enquote{Gyre} test field}
\label{gyre_volume}
\end{figure}
When we consider the volumes for the \enquote{gyre} test field, we can remark the holes, which represent the gyres in the centers of the volume for a low and a high threshold, whereby we extract (filter out) the previously observed ridges in $3D$ for all directions $\omega$ simultaneously.

Now, that the approach has passed the textbook examples, we push it forward to be applied in real (measured) data to show its performance in discerning and segmenting ROIs from a human brain. The approach will detect LCS in the brain's tissue from MRI-measured diffusion tensors of a male subject at the age of 27. We compare ParaView's glyph representation to the FTLE method LTG for the test field \enquote{brain}:
\begin{figure}[!t]
\centering
  \begin{minipage}[t]{0.3\textwidth}
  \includegraphics[height=\textwidth]{img/brain_cyl_glyphs.PNG}
    \caption*{a) glyph representation}
    \label{a)}
  \end{minipage}
  \begin{minipage}[t]{0.3\textwidth}
    \includegraphics[height=\textwidth]{img/brain_ftle.PNG}
     \caption*{b) LTG($0^\circ$)}
    \label{b)}
  \end{minipage}
  \begin{minipage}[t]{0.3\textwidth}
    \includegraphics[height=\textwidth]{img/brain_ftle_org.PNG}
     \caption*{c) FTLE: Hlawatsch's approach}
    \label{b)}
  \end{minipage}
  \caption{\enquote{Brain} test field}
\label{brain-ftle}
\end{figure}
Regarding Fig. \ref{gyre_volume}, we find that the approach detects the boundaries of concavities (lat.: Gyri) in the brain, forming the lobus cerebri (commonly known a lobes). The invented method could thus, e.g., aid to compute $3D$ models of a subject in medical sciences. It emphasizes regions with increased change in flow-rate (throughput), because in this areas the anisotropy and/or tensor magnitude is increased, preventing the intensities from being absorbed, hence yielding to a high FTLE-response. The regions highlighted in red, are caused by high tensor magnitudes, as we can infer from the glyph representation revealing no linear anisotropy at all. Note that we do not show the volume representation in this case, since all directions (slices) look approximately the same because the tensor field is only introducing changes in tensor magnitude not in anisotropy as inferred from the glyph representation. The regions with a tensor magnitude higher than zero restrict the light propagation to certain areas with the condition, that not all of the energy is absorbed by sorrounding cells in the local neighborhood. Again comparing the results to the classical FTLE (Hlawatsch's approach) on tensor fields in Fig. \ref{brain_ftle_comp}, we notice that the FTLE response is chaotic, since this MRI scan is subject to inherent MRI noise filling the background regions in the image. This noise produces random trajectories, leading to an increased gradient of the flow map and thus to a high FTLE response, which reveals trajectories running in random directions in background regions. Only in foreground regions, the trajectories are directed in definite manner, which is why the flow map's gradient is minimized along the brain structure (foreground, depicted in blue in Fig \ref{brain_ftle_comp} c)). Yet, our approach uses absorption to decrease noise present in the tensor field and reasonable min-max scaling to conduct $100\%$ of the intensity for the cell with the highest tensor magnitude. Hence, we do not yield a noisy representation but a FG-BG segmented image, with red highlights in positions, where the tensor magnitude is maximized (and thus absorption is minimized). Remark, that the resulting volume does not inherently depend on the direction, because the test field does not introduce any strong linear anisotropy, as visible from the glyph representation in Fig. \ref{brain_ftle_comp} a). If no linear anisotropy was incorporated, the FTLE response will also be independent on the direction to the greatest extent. The slices we obtain as our volume are, with reasonable explanation, more or less identical comparing them against each other for certain directions.

@@

\begin{figure}[!t]
\centering
  \begin{minipage}{0.3\textwidth}
  \centering
  \includegraphics[height=\textwidth]{img/heart.PNG}
    \caption*{a) LTG($0^\circ$): global}
    \label{a)}
  \end{minipage}
  \begin{minipage}{0.3\textwidth}
  \centering
    \includegraphics[height=\textwidth]{img_new/heart_slice0.PNG}
     \caption*{b) LTG($0^\circ$): local}
    \label{b)}
  \end{minipage}
  \begin{minipage}{0.3\textwidth}
  \centering
    \includegraphics[height=\textwidth]{img/heart_ftle_org.PNG}
     \caption*{c) Hlawatsch's approach}
    \label{b)}
  \end{minipage}
  \caption{\enquote{heart} test field}
\label{heart-ftle}
\end{figure}
After applying the LTG approach on the heart dataset, we observe the resulting tensor magnitude weighted FTLE-field, which is again not changing w.r.t. direction, which is why we do not show the volumes. The approach highlights the regions with diverging tensor field lines resulting from linear anisotropy or increased tensor magnitude, emerging as ridges. These ridges could now represent blood vessels and such. The red spot emphasized in the left of the image could, e.g., represent the highest diffusion velocity in tissue. When considering the FTLE for the heart dataset depicted in Fig. \ref{heart-ftle-comp}, we find that the trajectories exhibit strong correlations amongst them. This results from the low noise rate inherently present in this dataset. The inital value for our angle is given by $0$ degree, which is why the trajectories follow this angle strictly in case of a zero matrix (corresponding to a noise free cell in background regions). In this case, we obtain the same results as the approach from Hlawatsch et al., whereas our global min-max normalization (due to noise) is becoming a redundant step for noiseless input data. A proof of this elaboration can be found in Fig. \ref{heart-ftle-comp}.

@@

\begin{figure}[!t]
\centering
  \begin{minipage}{0.4\textwidth}
   \centering
  \includegraphics[width=\textwidth]{img_new/random-global.png}
    \caption*{Global normalization}
    \label{a)}
  \end{minipage}
  \begin{minipage}{0.4\textwidth}
   \centering
    \includegraphics[width=\textwidth]{img_new/random-local.PNG}
     \caption*{Local normalization}
    \label{b)}
  \end{minipage}
\caption{\enquote{Random} test field}
\label{random}
\end{figure}
Observing the generated random test field both with global and local normalization in Fig. \ref{random}a)\& b) respectively, we remark that the propability for small numbers to have a high ratio in combination is increased, as linear anisotropy occurs mainly in BG regions (low tensor magnitudes). In case we use global normalization in Fig. \ref{random_FTLE}a), we will again obtain a FTLE field independent on the direction, since tensor magnitudes outshine the changes in anisotropy in this test case. The LTG approach works as expected, as we see the tensor magnitude weighted into the left image, yielding a high response for the tensor magnitude weighted FTLE response.
\begin{figure}[!t]
\centering
  \begin{minipage}{0.4\textwidth}
   \centering
  \includegraphics[width=\textwidth]{img_new/random_global.png}
    \caption*{LTG: Global normalization}
    \label{a)}
  \end{minipage}
  \begin{minipage}{0.4\textwidth}
   \centering
    \includegraphics[width=\textwidth]{img_new/random_local_slice0.PNG}
     \caption*{LTG: Local normalization}
    \label{b)}
  \end{minipage}
\caption{\enquote{Random} test field}
\label{random_FTLE}
\end{figure}
In case we use local normalization in Fig. \ref{random_FTLE}b), we could interpret the contributions revealing low tensor magnitudes as a result from white noise, which shows the inherent problem with local normalization. If we would just locally normalize the whole tensor field with the mean tensor magnitude of each cell, we would enhance noisy contributions, which turn out to be in general more propable to be anisotropic than FG data. Keeping this consideration in mind, we observe the approach detecting raw changes in anisotropy. Note, that this test field does not introduce clearly defined ridges with tensor field lines diverging w.r.t. to a middle axis. We just introduce rapid random variations in anisotropy along the spatial domain, which is why the FTLE response is independent on the direction in this case, as well. This example emphasizes, that ridges can also be yielded from rapid changes in anisotropy and are hence in this case, not directed and thus non directionally dependent. Also we take home from this example, that the thresholding is in fact necessary to form a reasonable local normalization as a posteriori verification.

@@

Please note that all values in the test table where measured on following system:\\
\texttt{4 x 16-Core Gold 6142M 2.60GHz, 3072 GB RAM}.
\begin{table}
\small
\centering
\caption{Test Table LTG:}
\begin{tabularx}{\columnwidth}{X|X|X|X}
\hline\hline
test name - Fig. \# & resolution ($x\times y\times\omega$) & runtime $[s]$ & memory consumption (dynamic)\\
\toprule
\enquote{drain} - \ref{ftle_base} & $101\times101\times64=652864$ & $179878$ & $8\times652864\times 8\mathop{byte} +(101\times101 + 19\times64)\times8\mathop{byte}\approx47.02\mathop{MB}$\\ 
\hline 
\enquote{inverse} - \ref{inverse-ftle} & $101\times101\times64=652864$ & $68787$ & $8\times652864\times 8\mathop{byte} +(101\times101 + 19\times64)\times8\mathop{byte}\approx47.02\mathop{MB}$\\
\hline 
\enquote{random} &  &  & \\ 
\hline 
\enquote{isotropic} - \ref{bow-ftle} & $51\times51\times3283232$ & $1357$ & $8\times83232\times 8\mathop{byte} +(51\times51 + 19\times32)\times8\mathop{byte}\approx5.998\mathop{MB}$\\ 
\hline
\enquote{rings} - \ref{bow-ftle} & $51\times51\times32=83232$ & $5761$ & $8\times83232\times 8\mathop{byte} +(51\times51 + 19\times32)\times8\mathop{byte}\approx5.998\mathop{MB}$\\ 
\hline 
\enquote{bow} - \ref{bow-ftle} & $51\times51\times32=83232$ & $6128$ & $8\times83232\times 8\mathop{byte} +(51\times51 + 19\times32)\times8\mathop{byte}\approx5.998\mathop{MB}$\\ 
\hline 
\enquote{star} - \ref{star-ftle} & $51\times51\times32=83232$ & $5815$ & $8\times83232\times 8\mathop{byte} +(51\times51 + 19\times32)\times8\mathop{byte}\approx5.998\mathop{MB}$\\ 
\hline 
\enquote{inverse} - \ref{inverse-ftle} & $101\times101\times16=163216$ & $12308$ & $8\times163216\times 8\mathop{byte} +(101\times101 + 19\times16)\times8\mathop{byte}\approx11.754\mathop{MB}$\\ 
\hline 
\enquote{inverse} - \ref{inverse-ftle} & $101\times101\times32=326432$ & $24571$ & $8\times326432\times 8\mathop{byte} +(101\times101 + 19\times32)\times8\mathop{byte}\approx23.5\mathop{MB}$\\ 
\hline
\enquote{brain} - \ref{brain-ftle} & $128\times128\times64=1048576$ & $2427$ & $8\times1048576\times 8\mathop{byte} +(128\times128 + 19\times64)\times8\mathop{byte}\approx75.5\mathop{MB}$\\
\hline
\enquote{heart} - \ref{heart-ftle} & $256\times256\times32=2097152$ & $117199$ & $8\times2097152\times 8\mathop{byte} +(256\times256 + 19\times32)\times8\mathop{byte}\approx151.0\mathop{MB}$\\
\hline 
\end{tabularx}
   \vskip 1pt
\end{table}
